pema application

### 2022-11-28 paper/action_letter.Rmd
update 2022-11-28 13:44:48

---
title       : "Selecting relevant moderators with Bayesian regularized meta-regression"
authors     : "masked"
journal     : "Research Synthesis Methods"
editor      : "Pigott"
manuscript  : "RSM-04-2022-0056"
class       : "draft"
bibliography      : ["r-references.bib", "references.bib",
                     "sara-references.bib", "eli-references.bib", "metaforest.bib"]
output      : papaja::revision_letter_pdf
---

```{r, message=FALSE, warning=FALSE}
library(revise)
read_manuscript("manuscript.Rmd")
```

@@

In addressing all comments below, we have added detail and elaboration in many places. We hope that this addresses this comment.

@@

We see now that we did not report clearly enough how many design factors there were and what they were.
Apparently, it was also not sufficiently clear that "noise moderators" are not the same as "design factors".
To address this comment and avoid confusion, we have rewritten this paragraph as follows:

@@

To address this comment, we have made the following changes:

1) We have rewritten the opening paragraph to clearly state the problem addressed in this paper, and the proposed solution:

@@

\WorkInProgress

@@

\WorkInProgress

@@

\WorkInProgress

@@

\WorkInProgress

@@

\WorkInProgress

@@

\WorkInProgress

@@

\WorkInProgress

@@

\WorkInProgress

@@

\WorkInProgress

@@

\WorkInProgress

@@

We intended to explain that the regularizing horseshoe prior is an extension of the (normal) horseshoe prior. This was insufficiently clear.
To address this comment, we have written the following section:

@@

To address this comment, we have made a stricter separation between methodology and code. 
All references to code are now relegated to the Implementation section.

We do believe that there are advantages to having code in the paper and not in an appendix, as the intended readership for this paper consists of those who wish to conduct a Bayesian regularized meta-analysis. We hope that the current approach is an acceptable compromise.

@@

This section is important because omitting the intercept from the model has very different implications for penalized Bayesian meta-regression than for frequentist models (where the model is equivalent, regardless of whether the intercept is included or not).

@@

`get_revision("intercept")`

@@

We respectfully believe that this comment is based on a misunderstanding of the procedure.
We do not split a finite sample into a training and testing set - 
we simulate data for both sets from the same known data generating model.
Each sample from this model is independent and identically distributed (IID).
The distinction between training and testing is thus arbitrary.
This is different from real data analyses, where the available dataset is finite, and training and testing data are drawn from that finite dataset - thus violating the assumption of IID.

@@

We respectfully feel that it is important to define how we operationalized each outcome metric, and why we use it.
Unfortunately, we now realize that our explanation was not sufficiently clear. To address this comment, we have rewritten the explanation of our outcome metric, $R^2_{test}$. We hope that this revised explanation clarifies that this is **not** the basic indicator R2, but rather, a different type of R2 that is suitable for assessing overfitting:

@@

Additionally,
the reason we do not use AIC or BIC is because these are comparative fit indices, only suitable for comparing a set of models; we have only a single model and AIC or BIC do not speak to the absolute fit of a single model.

The reason we do not use adjusted $R^2$ is because it is an approximation of $R^2_{test}$ but calculated on the training sample data.
Since we simulate data from a known true model,
we do not need to *estimate* $R^2_{test}$ - we can *calculate* it directly, based on a new sample.

@@

As these simulations are very computationally demanding,
and increasing the number of replications adds only marginal accuracy gains, we did indeed use 100 replications.
However, as per the Reviewer's request, we have increased this to 1000.

@@

We corrected this, and slightly rephrased the sentence for clarity.

@@

To address this comment, we now describe the results in the text, and provide the requested tables as online Supplements.

@@

The reason we used these data is because we were able to secure permission from the original author to include them in the R-package.
This means we can make the examples reproducible, requiring only the `pema` package.
We feel that it adds a lot to the paper to present a reproducible real-data example based on a novel dataset.
To address this comment,
we now acknowledge in the text that this sample is relatively large compared to the sample sizes of the simulation study:

\WorkInProgress

@@

\WorkInProgress

@@

\WorkInProgress

@@

We thank the Reviewer for suggesting these references, which had eluded our literature search.

We agree that the use of weakly informative priors for heterogeneity parameters was insufficiently discussed in the previous version of our manuscript, and have now added a paragraph on that topic (see our response to the next comment).

However, it is important to note that the use of weakly informative priors (WIP) for heterogeneity parameters serves a categorically different purpose than the use of regularizing priors for regression coefficients - even if the term "regularization" has been used for both in prior literature.
The purpose of WIP for heterogeneity parameters is to aid model convergence and avoid boundary estimates.
The purpose of regularizing priors for regression coefficients is to perform variable selection.
We believe that the newly added paragraph sufficiently clarifies these distinct uses of "regularization" (see response to next comment).

Thank you for pointing out these relevant references. We have included the reference to Chung et al. (2013), Gelman (2006) and Rover et al. (2021) in the new section on the prior for $\tau$ (see the next comment). In addition we have added the following section on page ... to be more explicit about the terminology of different types of priors:

Suggest to add this paragraph in the section on Bayesian estimation after "which reflects expectations about likely parameter values after having seen the data." Note: if included, this should be updated in the text from a previous comment to reviewer 1 as well. Also here it is relevant whether we use "regularizing" or "shrinkage" priors and should mention the definite choice explicitly.

"As a result, the posterior distribution is a compromise between the likelihood of the data and the prior distribution. The influence of either the data or the prior is determined by the sample size as well as the informativeness of the prior distribution. The larger the sample size, the more influential the likelihood of the data will be. Similarly, as the prior distribution becomes more informative, i.e., more peaked, it will exert more influence on the results. Priors can thus be placed on a continuum from "non-informative" to "highly informative". Weakly informative or regularizing priors are often used in situations when there is some prior information available, for example regarding the boundaries of the parameter space or, as is the case here, regarding the existence of parameters equal to zero. Throughout this manuscript, we will use the term "shrinkage prior" to refer to the weakly informative or regularizing prior that holds the prior knowledge that some coefficients are equal to zero and should therefore be shrunken towards zero."

\WorkInProgress

@@

Chung Y, Rabe-Hesketh S, Choi IH. Avoiding zero between-study variance estimates in random-effects meta-analysis. Stat Med. 2013;32(23):4071-4089.

Gelman A. Prior distributions for variance parameters in hierarchical models. Bayesian Anal. 2006;1(3):515-534. [https://doi.org/10.1214/06-BA117A](https://doi.org/10.1214/06-BA117A "https://doi.org/10.1214/06-BA117A").

Gronau, Q. F., Van Erp, S., Heck, D. W., Cesario, J., Jonas, K. J., & Wagenmakers, E. J. (2017). A Bayesian model-averaged meta-analysis of the power pose effect with informed and default priors: The case of felt power. _Comprehensive Results in Social Psychology_, _2_(1), 123-138.

Röver, C, Bender, R, Dias, S, et al. On weakly informative prior distributions for the heterogeneity parameter in Bayesian random-effects meta-analysis. Res Syn Meth. 2021; 12: 448– 474. [https://doi.org/10.1002/jrsm.1475](https://doi.org/10.1002/jrsm.1475 "https://doi.org/10.1002/jrsm.1475")

@@

# References
1) Thompson SG, Higgins JPT. How should meta-regression analyses be undertaken and interpreted?. Stat Med. 2002;21:1559-1573.
2) Chung Y, Rabe-Hesketh S, Choi IH. Avoiding zero between-study variance estimates in random-effects meta-analysis. Stat Med. 2013;32(23):4071-4089.
3) Günhan, BK, Röver, C, Friede, T. Random-effects meta-analysis of few studies involving rare events. Res Syn Meth. 2020; 11: 74– 90. https://doi.org/10.1002/jrsm.1370
4) Röver, C, Bender, R, Dias, S, et al. On weakly informative prior distributions for the heterogeneity parameter in Bayesian random-effects meta-analysis. Res Syn Meth. 2021; 12: 448– 474. https://doi.org/10.1002/jrsm.1475
5) Gelman A. Prior distributions for variance parameters in hierarchical models. Bayesian Anal. 2006;1(3):515-534. https://doi.org/10.1214/06-BA117A.

>>>>

---
title       : "Selecting relevant moderators with Bayesian regularized meta-regression"
authors     : "masked"
journal     : "Research Synthesis Methods"
editor      : "Pigott"
manuscript  : "RSM-04-2022-0056"
class       : "draft"
bibliography      : ["meta-analysis.bib"]
output      : papaja::revision_letter_pdf
---

```{r, message=FALSE, warning=FALSE}
library(revise)
library(tidySEM)
out <- readRDS("output.RData")
read_manuscript("manuscript.Rmd")

```

@@

We have rewritten all sections of the paper and restructured some of them. Furthermore, in addressing all reviewer comments (see below), we have added detail and elaboration in many places. We hope that this addresses this comment.

@@

We see now that we did not report clearly enough how many design factors there were and what they were.
To address this comment and avoid confusion, we have rewritten this paragraph as follows:

@@

To address this comment, we have rewritten the opening paragraph to clearly state the problem addressed in this paper, and the proposed solution:

@@

@@

We have merged several sections to avoid repetition in the text.

@@

We have attempted to clarify this sentence as follows:

`r get_revision("informationdistribution")`

@@

To address this comment, we have moved the explanation of the "error term" to the paragraph where it is first discussed.

@@

To address this comment, we have moved this paragraph about regularization into the section on regularized regression.

@@

Our aim is to provide a high-level conceptual introduction of the method's underpinnings,
not to replicate the many excellent technical publications that already exist on these methods. 
To address this comment, we have edited all technical sections for greater clarity and detail. Additionally, we explicitly direct the reader to appropriate introductory texts that go more in depth:

`r get_revision("reftibshirani")`

And:

`r get_revision("refmcelreath")`

@@

We were not aware of any existing literature at the time of writing;
most likely because several such papers were only published after we wrote our draft - but we thank the Reviewer for encouraging us to search the literature again. Based on our findings, we now include the following paragraph:

`r get_revision("earlierpapers")`

@@

To address this comment, we now cite the following theoretical paper:

`r get_revision("reftibshirani")`

@@

We respectfully feel that indicating advantages and disadvantages of other penalties is out of scope for the present paper.
The only reason we explain the LASSO penalty is to explain how regularization works.
Since we ultimately do not use a frequentist solution with shrinkage penalties, there is little point to explaining other penalties in detail.

To address this comment, we now clarify why we explain the LASSO penalty:

`r get_revision("whylasso")`

@@

We now explain this as follows:

`r get_revision("defaultvalues")`

Note that the results of our simulation study again validate the fact that these are sensible defaults.

@@

We recognize that this choice of words was confusing.
The regularizing horseshoe prior is an extension of the horseshoe prior.
To address this comment, we now explain this in the text:

@@

We see that a stricter separation of methodology and code could aid readability.
Therefore, we have addressed this comment by relegating all code to the Implementation section.

We do believe that there are advantages to having code in the paper and not in an appendix,
as the intended readership for this paper consists of those who wish to conduct a Bayesian regularized meta-analysis. For this purpose, it is important that readers understand how to translate the methodological principles to a model specified in the `pema` package.
We hope that the current revision strikes a reasonable compromise.

@@

This section is important because omitting the intercept from the model has very different implications for regularized meta-regression than for non-regularized models.

@@

`r get_revision("intercept")`

@@

We respectfully believe that this comment is based on a misunderstanding of the procedure.
The Reviewer's comment seems to suggest that we split a finite sample into a training and testing set. This is not the case.

Instead, we simulate both data sets from the same known data generating model.
Each sample from this model is thus independent and identically distributed (IID).
The distinction between training and testing is arbitrary.
This is different from real data analyses, where the available dataset is finite, and training and testing data are drawn from that finite dataset - thus violating the assumption of IID.

@@

We respectfully feel that it is important to define how we operationalized each outcome metric, and why we use it.
In fact, it seems that our explanation was not sufficiently clear,
because the outcome metric is not the basic indicator R2,
as the Reviewer has apparently understood,
but rather, a different type of R2 that is suitable for assessing overfitting.

To address this comment, we have tried to explain the outcome metric, $R^2_{test}$ more clearly:

@@

With regard to the Reviewer's suggestion to use AIC or BIC:
the reason we do not use these is because they are comparative fit indices, only suitable for comparing a set of models; we have only a single model and AIC or BIC do not speak to the absolute fit of a single model.

The reason we do not use adjusted $R^2$ is because it is an approximation of $R^2_{test}$ that can be calculated on the training data.
Since we can simulate testing data from a known model,
we do not need to *estimate* $R^2_{test}$ - we can *calculate* it directly.

@@

As reported, we used 100 replications per simulation condition because these simulations are very computationally demanding,
and increasing the number of replications adds only marginal accuracy gains.
In total, we thus simulated 194.400 cases.
Many of the analyses marginalize over some design factors,
thus we always have a very large sample size.
We do not see an urgent need to increase the number of replications,
but we defer to the Editor in this matter.

@@

We corrected this, and have rephrased the sentence for clarity.

@@

To address this comment, we now describe the results in the text, and provide the requested tables as online Supplements:

`r get_revision("variancebeta")`

And:

`r get_revision("variancetau")`

@@

The reason we used these data is because we were able to secure permission from the original author to include them in the R-package.
This means we can make the examples reproducible, requiring only the `pema` package.
We feel that it adds a lot to the paper to present a reproducible real-data example based on a novel data set.
To address this comment,
we now acknowledge in the text that this sample is relatively large compared to the sample sizes of the simulation study:

`r get_revision("sample400")`

@@

We have proofread and spell checked the manuscript, and corrected all mistakes found.

@@

We agree with the Reviewer that there are important limitations to meta-regression, and Thompson & Higgins provide an excellent analysis thereof.
<!-- Limitations -->
<!-- i) multicolinearity -->
<!-- ii) ecological fallacy -->
<!-- iii) restriction of range -->
<!-- iv) multicolinearity -->
<!-- v) something specific to clinical trials?? -->
<!-- vi) data availability -->
<!-- vii) small sample size, limited generalizability -->
<!-- PITFALLS -->
<!-- i) curse of dimensionality: small sample size, multicolinearity -->
<!-- ii) overfitting -->
<!-- iii) variable selection -->
<!-- iv) variable selection -->
Most of the limitations and pitfalls they discuss come down to two fundamental points which are already addressed throughout our paper: 1) the curse of dimensionality and its implications for multicolinearity (limitations i, iv, vii and pitfalls i, ii, iii, and iv), and 2) the ecological fallacy (limitation ii and iv).
They further address three singular points which cannot be attributed to the two fundamental points:
Limitation iii relates to the problem of restriction of range in moderators (which we do not address),
Limitation vi relates to limited data availability (which we address in our discussion of missing data),
and Limitation v makes a point about regression to the mean in RCTs that we fail to grasp.

Since our method is a statistical solution to point 1),
we devote most attention to it.
We also acknowledge most of the other points.
However, we respectfully feel that it is out of scope for the present paper to devote further attention to limitations of meta-regression that our method does *not* address;
especially since Thompson & Higgins already did so.

To address this comment, we have referenced the Thompson & Higgins paper in several places, and we have added the following sentences to our Recommendations for Applied Researchers:

`r get_revision("metareglimits")`

@@

First of all, we thank the Reviewer for suggesting these references, which had eluded our literature search.
We now cite them in relevant places in the manuscript.

Second of all, we agree that the use of weakly informative priors for heterogeneity parameters was insufficiently discussed in the previous version of our manuscript, and have now added a paragraph on that topic (see our response to the next comment).

Third of all, we feel that it is important to stress that the use of weakly informative priors (WIP) for heterogeneity parameters serves a categorically different purpose than the use of regularizing priors for regression coefficients - even if the term "regularization" has been used for both in prior literature.
The purpose of WIP for heterogeneity parameters is to aid model convergence and avoid boundary estimates.
The purpose of regularizing priors for regression coefficients is to perform variable selection.
We believe that the newly added paragraph sufficiently clarifies these distinct uses of "regularization" (see response to next comment).

@@

@@
